\section*{Sendiv}
\textit{\textbf{Captain's Log:} We have arrived at Sendiv, an independent city state that was recently admitted to the Interstellar Confederation. Renowned for its natural beauty, the city sits atop an island on a watery moon of a spectacular gas giant.}

\textit{We are here at the request of the Sendivian city council. A child has been abducted from one of their schools. They have asked us to help find the child and ensure her safe return.}

\textit{Citing privacy concerns, the Sendivians have requested that we not use the Endeavour's sensors to indiscriminately scan the city. We're going to have to do this the old-fashioned way.}

\subsection*{Arrival}
You are directed to Police Headquarters. The building is filled with harried police officers trying to manage the crisis. 

\textbf{Garnat}, the police chief, tells you that the city's residents have been directed to return to their homes and remain there until further notice. No justification has been provided.

\textbf{Tzalikin}, the missing child's estranged father, also seems to be missing.  Garnat suspects Tzalikin may have kidnapped his daughter. A warrant has been issued for his arrest.

\subsubsection*{Title for the Arrival Challenge}
\begin{itemize}
	\item \textit{Will you help Garnat to secure the city?} \textbf{Operations \& Engineering} vs \textbf{Security} (3d8). If you fail, then Tzalikin gains a 1d10 advantage die on all challenges.
	\item \textit{Will you try to convince Garnat to allow you to utilize the Endeavour's sensors?} \textbf{Leadership \& Negotiation} vs. \textbf{Garnat}. This is a \textit{Fraught} challenge \textemdash{} The Sendivians care deeply about personal privacy. If you prevail you gain a 1d10 advantage die on all challenges vs. Tzalikin.
\end{itemize}
\newpage

\subsection*{Trials}
\subsubsection*{The Invisible Man}
Garnat calls you to his office He introduces you to a woman who claims that she saw doors opening and furniture moving, apparently on their own, near the school shortly after the child was abducted.  \textit{Can you figure out how to see through Tzalikin's disguise?}  \textbf{Science \& Medicine} vs. \textbf{Tzalikin}.

\subsubsection*{False Alarm}
A klaxon sounds throughout the city accompanied by flashing lights and an automated announcement.

\textit{Emergency! A radiation leak has been detected. Evacuate the city immediately. Repeat, evacuate the city immediately.}

Emergency protocols are activated and the lockdown is lifted. \textit{Can you prevent Tzalikin from escaping in the ensuing confusion?} \textbf{Strategy \& Tactics} vs. \textbf{Tzalikin}

\subsubsection*{Peace Offering}
Tzalikin contacts the police. He tells them that he has made a terrible mistake and that he has released his daughter. She is waiting to be picked up at the water recycling plant. \textit{Will you try to determine where he is calling from?} \textbf{Operations \& Engineering} vs. \textbf{Tzalikin}.

\subsection*{Crisis}
\begin{itemize}
	\item \textit{Will you physically confront Tzalikin?} \phantom{a} \\ \textbf{Threats:} Tzalikin makes a risky getaway via the utility corridors. If cornered, he detonates an explosive device rather than surrender.
	\item \textit{Or will you try to negotiate with Tzalikin?} \phantom{a} \\ \textbf{Threats:} Tzalikin takes hostages and demands safe passage off of Sendiv. He starts killing hostages if his demands are not met.
\end{itemize}

\newpage

\subsection*{Characters}
\begin{description}
	\item[Tzalikin (d8):] Estranged Father (d6), Extremist (d8), Unstable (d6), Violent (d6 \textit{Dangerous}).
	\item[Garnat (d8):] Police Chief of Sendiv (d8), Principled (d8), Experienced (d6), Dedicated (d6).
\end{description}

\subsection*{Places}
\begin{description}
	\item[Police Headquarters:] A municipal office building. Each floor is dominated by an open-plan bullpen. Senior officers have private offices around the periphery.
	\item[Water Reclamation Plant:] A clean and modern industrial area buried deep in the bowels of the city.
\end{description}

\subsection*{Special Rewards}
\begin{description}
	\item[Tzalikin's Stealth Shield:] A personal-scale stealth shield which conceals its user from all forms of detection.
\end{description} 

\subsection*{Mysteries}
\begin{description}
	\item[Sendivian law emphasizes the right to privacy.] \phantom{a} \\ The Sendivians recently suffered under the rule of an authoritarian surveillance state. \textit{How do the Sendivians prevent their city from becoming hotbed of illicit activity? Has it already happened?  How would they know?}
	\item[Tzalikin is using a personal-scale stealth sheild.] \phantom{a} \\ Stealth shields consume huge amounts of energy. Until now, stealth shields only existed as ship-scale devices. \textit{Who designed Tzalikin's personal-scale stealth shield? What does it use as a power source?}
\end{description}